Parametric controls on vegetation responses to biogeochemical forcing in the CLM5

### 2019-06-28 main_revision.tex

\subsubsection{Water and N limitation across sites}
The four sites varied in the degree to which they are limited by water and N availability in the control state, with important impacts upon the parametric response characteristics (Figure \ref{btran state}). Water limitation in CLM5 can be expressed via the $B_{tran,mn}$ parameter, which is a model property calculated as a function of the prognostic leaf water potential. $B_{tran}$  is used to reduce assimilation and thus stomatal conductance by scaling the photosynthetic capacity, $V_{c,max}$. Leaf water potential and  $B_{tran}$ vary diurnally, so we use the average daily minimum value here as a metric of drought stress (1 is no drought stress, 0 is total stomatal closure). For N limitation, the fraction of total NPP (where NPP is GPP-$r_{auto}$) that is used to pay for nitrogen uptake is a direct indicator of how N stress affects the carbon budget.

The Caxiuan\~a site experienced substantial drought stress in these simulations (with the mean $B_{tran,mn}$ of the default condition around $\sim$0.55), with little nutrient stress. The simulated forest at Niwot Ridge experienced substantial amounts of drought ($B_{tran,mn}$ $\sim$0.5), and N limitation, spending 27\% of net assimilated carbon on nutrient acquisition. Harvard Forest site had a moderate drought stress ($B_{tran,mn}$ $\sim$90\%), and moderate N limitation ($\sim$15\% of assimilation spent on uptake). The Metolius site had some drought stress ($B_{tran,mn}$ $\sim$86\%) and very little nutrient stress.  Differences in the initial conditions at the sites have implications for the parametric responses. Underlying limitations by various boundary conditions (water, nutrients, light, temperature) can affect both the ability of the system to respond to fertilization and/or parameter modifications affecting other resources, as we describe further in the following sections.

@@

As expected from the initial conditions, Niwot Ridge responded most strongly to nutrient additions. An initial NPP stimulation of 1.3 for NPP was magnified by subsequent increases in LAI to nearly 1.8 times the control value, causing a stimulation of 1.7 in NPP. None of the other sites exhibited such a dramatic change. In particular, Caxiuana, which was heavily water limited in the first instance, adding nitrogen only resulting in stimulation in LAI, GPP and NPP of around 10\%.

The time-dependence of the responses generates an interesting issue for interpretation, since where LAI increases a lot, the responses tend to be dominated by this feature of the response. The first year responses, by way of contrast, tend to be much more similar across sites, parti.

>>>>

\subsubsection{Water and N limitation across sites}
The four sites varied in the degree to which they are limited by water and N availability in the control state, with important impacts upon the parametric response characteristics (Figure \ref{btran state}). Water limitation in CLM5 can be expressed via the $B_{tran,mn}$ parameter, which is a model property calculated as a function of the prognostic leaf water potential. $B_{tran}$  is used to reduce assimilation and thus stomatal conductance by scaling the photosynthetic capacity, $V_{c,max}$. Leaf water potential and  $B_{tran}$ vary diurnally, so we use the average daily minimum value here as a metric of drought stress (1 is no drought stress, 0 is total stomatal closure). For N limitation, the percentage of total NPP (where NPP is GPP-$r_{auto}$) that is used to pay for nitrogen uptake (PNU) is a direct indicator of how N stress affects the carbon budget.

The Caxiuan\~a site (CAX) experienced substantial drought stress and little nutrient stress ($B_{tran,mn}$ $\sim$0.6, PNU$\sim$13\%). Niwot Ridge (NWR) experienced substantial amounts of drought and N limitation, ($B_{tran,mn}$, $\sim$0.55, PNU$\sim$21\%). Harvard Forest (HVF) site had very little drought stress, and moderate N limitation ($B_{tran,mn}$ $\sim$0.96, PNU$\sim$15\%).  Metolius (MET)  had some drought stress and the least nutrient stress ($B_{tran,mn}$ $\sim$0.86, PNU$\sim$10\%).  
Thus, the sites chosen span a range of initial limiting conditions.

Differences in the initial conditions at the sites have implications for the parametric responses. Underlying limitations by various boundary conditions (water, nutrients, light, temperature) can affect both the ability of the system to respond to fertilization and/or parameter modifications affecting other resources, as we describe further in the following sections.

@@

As expected from the initial conditions, Niwot Ridge responded most strongly to nutrient additions. An initial NPP stimulation of 1.3 for NPP was magnified by subsequent increases in LAI to nearly 1.8 times the control value, causing a stimulation of 1.7 in NPP. None of the other sites exhibited such a dramatic change. In particular, Caxiuana, which was heavily water limited in the first instance, adding nitrogen only resulting in stimulation in LAI, GPP and NPP of around 10\%. Stimulation at Metolious was higher than Caxiuana, despite it's lower initial N limitation, given it's lack of limitation by water.

The time-dependence of the responses generates an interesting issue for interpretation, since where LAI increases a lot, the responses tend to be dominated by this feature of the response. The first year responses, by way of contrast, tend to be much more similar across sites.
